A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
candidates captions

\begin{figure}[p]
\begin{center}
\includegraphics{figures/candidates.pdf}
\end{center}
\caption{%
\figlabel{candidates}}
\end{figure}

@@

\begin{table}[p]
\begin{center}
\small
\include{tab-cand}
\end{center}
\caption{%
Candidates
\tablabel{cand}}
\end{table}

>>>>

\begin{figure}[p]
\begin{center}
\includegraphics{figures/candidates.pdf}
\end{center}
\caption{%
The \emph{a posteriori} distribution of planet candidates in the catalog.
The error bars indicate the 0.16 and 0.84 posterior sample quantiles for the
radius ratios.
\figlabel{candidates}}
\end{figure}

@@

\begin{table}[p]
\begin{center}
\small
\include{tab-cand}
\end{center}
\caption{%
The catalog of planet candidates and their observable properties.
These values and their uncertainties are derived from MCMC samplings and the
numbers are computed as the 0.16, 0.5, and 0.84 posterior sample quantiles.
\dfmtodo{RA/Dec coords.}
\tablabel{cand}}
\end{table}
